Optimizing the Robotics Closet

### 2018-11-16 paper.tex
add buncha shit idk like the bs at the end and shit fuck

\section{Conclusions}

\section{Acknowledgements}

>>>>

\section{Conclusions}
In conclusion, we are happy to have found an integer programming approach with the aforementioned constraints and objective function to be successful at finding a reasonably optimal arrangement of items. We were able to learn the practical challenges of solving a real-world linear programming problem, whilst still getting a result that has legitemate applications.

\section{Acknowledgements}
We would like to thank:
- Dr. Sara Billey for providing us with guidance throughout the project,
- Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
- UW Husky Robotics for providing the closet to undergo optimization,
- Nolan Donovan for working with us to understand and solve this problem.
